Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-01-30 text/front_end_v2.qmd
tweaker

@@

>>>>

**ABSTRACT**

In 1984, the College Board created "Geomarkets," which carve states and metropolitan areas into smaller geographic units meant to define local recruiting markets. Geomarkets are an input in two College Board products. First, the Enrollment Planning Service (EPS) software makes recommendations about which Geomarkets and high schools admissions recruiters should recruit from. Second, Geomarkets became a search filter within the Student Search Service product, which enables colleges to buy "student lists" containing the contact information of prospective students. The concept of Geomarkets was introduced by *The Structure of College Choice* [@RN4982]. This book develops the "Market Segment Model," which argues that student demand for a particular college is a function of class and geography. We conceptualize Geomarkets and the Market Segment Model by drawing from scholarship on quantification, particularly the discussions of correlation and homophily by @RN4975. We address two research questions: First, what is the socioeconomic and racial variation between Geomarkets and how does this variation change over time? Second, how does the socioeconomic and racial composition of included versus excluded prospects vary when student list purchases filter on particular Geomarkets? We answer RQ1 by analyzing Census data from 1980, 2000, and 2020. We answer RQ2 by analyzing data from actual student lists purchased by public universities. Metropolitan areas are cases. Analyses consist of graphs of descriptive statistics and interactive maps.

@@

@list_empirics say this:
